---
title: "Researcher Variability in Replications: Replication File, Step 1"
output: html_document
---

This project uses data from the Crowdsourced Replication Initiative ([CRI](https://osf.io/preprints/socarxiv/6j9qb/)). This represents the first stage where reseracher participants had to replicate a study by Brady and Finnigan ([2014](https://doi.org/10.1177/0003122413513022)). The teams consisted of 1-3 members and were randmly divided into two groups,  one with the original study,  paper and code and the other with only a anonymized methods section,  no knowledge of the original study (or link to it in their work) and no code. 

Datafiles needed 

| File | Description |
|------|-------------|
| cristageone.xlsx | Results of the CRI in raw format; odd-ratios, significance and deviance from original,  as the teams submitted them |
| cristageone.cur1.xlsx | Results after code curation |
| cri_survey_wide_public_nolabs.dta | Survey of the replicators |
| teamsize.csv | Datafile containing teamsize and primary software used |



```{r setup}

rm(list = ls())
library(pacman)

pacman::p_load("readstata13", "dplyr", "readr", "lattice", "tidyr", "readxl", "knitr", "boot", "ragg", "kableExtra", "lavaan", "lavaanPlot")

#Column no missing function
completeFun <- function(data,  desiredCols) {
  completeVec <- complete.cases(data[,  desiredCols])
  return(data[completeVec,  ])
}


```

## Load Data

### Replication Results

Two teams submitted two different result sets,  therefore,  we need to give them unique team identifiers for the analytical phase

```{r rep_data}

cri <- read_xlsx("data/cristageone.xlsx")
cri_cur <- read_xlsx("data/cristageone.cur1.xlsx")

cri$u_teamid <- cri$`Team ID` 
cri_cur$u_teamid <- cri_cur$`Team ID`

# unique IDs for two-result teams
cri <- cri %>%
  mutate(u_teamid2 = ifelse(u_teamid == 70 & (u_teamid - lag(u_teamid,  n = 1L)) == 0,  701,  u_teamid), 
         u_teamid2 = ifelse(u_teamid == 101 & (u_teamid - lag(u_teamid,  n = 1L)) == 0,  1001,  u_teamid2))

cri_cur <- cri_cur %>%
  mutate(u_teamid2 = ifelse(u_teamid == 70 & (u_teamid - lag(u_teamid,  n = 1L)) == 0,  701,  u_teamid), 
         u_teamid2 = ifelse(u_teamid == 101 & (u_teamid - lag(u_teamid,  n = 1L)) == 0,  1001,  u_teamid2))


```


### Participant Survey

Original work up of individual/team researcher qualities done in Stata

NOTE: These Stata files include identifying information breaking the anonymity of the teams,  so we have to clean them before making them public. The CRI provided a file with the cleaned and merged data "cri_survey_wide_public_nolabs.dta" and its raw data (without labels) version with "cri_survey_wide_public_nolabs.dta"

This was created from the following:

Required code files:
  master.do
      convert spss.do
      merge_waves.do
      recode.do
  Cri_spec.do

Required SPSS data files:
  W1_export.sav
  W2_export.sav
  W3_export.sav
  W4_export.sav
  
The above files contain personal identifiers and are therefore not allowed for public use. 
  
Note that teams are now in wide format,  so that each variable has up to three values,  one for each team member. Also,  each result is attached to each team member,  thus there are N-results repeated observations of team members.



```{r survey,  warning=F,  message=F }

# datafile merged into within-team wide format

cri2 <- readstata13::read.dta13("data/cri_survey_wide_public_nolabs.dta")

```


### Set up Measurement Variables

Team max used for statistics skills and mean for difficulty of replication. The logic is that as long as each team member took part in production of the final product,  the one with the highest skills will apply those skills before accepting it. Also,  even if it was very difficult for some team members (maybe because they had to learn software,  routines,  code,  etc.),  it may have been easy for others because the one with greater skills had to do more work; we think it more accurate to take the mean as a result of this risk. 


```{r recodes,  warning=F,  message=F}

#Generate team-specific qualities

# Because the CRI required teams to define the data-generating model (or at least a test of it) and use statistical competencies to carry it out,  we suspect that the highest statistical and topical knowledge and experience per team will have the greatest influence on the results. Therefore,  for the concepts 'Stats Level' and 'Topic Level' we take the row min or max for each team (depending on coding. 


cri2 <- cri2 %>%
  rowwise() %>%
      mutate(stat3 = -1*(max(v_341,  v_342,  v_343,  na.rm = T)),  #higher is less dificult replication
             stat4 = mean(c(backgr_exp_teach_stat1,  backgr_exp_teach_stat2,  backgr_exp_teach_stat3),  na.rm = T),  #higher more courses taught
             stat5 = mean(c(backgr_exp_famil_mlm1,  backgr_exp_famil_mlm2,  backgr_exp_famil_mlm3),  na.rm = T),  #higher more MLM familiarity
             stat6 = mean(c(v_181,  v_182,  v_183),  na.rm = T),  #higher is more stat publications
             stat7 = mean(c(v_211,  v_212,  v_213),  na.rm = T), #higher is more MLM publications
             degree = ifelse(backgr_degree1 == 3, 1, ifelse(backgr_degree1 == 4, 2, 3)),
             degree2 = ifelse(backgr_degree2 == 3, 1, ifelse(backgr_degree2 == 4, 2, 3)),
             degree = ifelse(is.na(backgr_degree1) | backgr_degree1 == 7, degree2, degree))

cri2$degree <- as.numeric(ifelse(is.na(cri2$degree), 3, cri2$degree))

# replace -Inf values with NA

cri2 <- cri2 %>%
  ungroup() %>%
  mutate(stat3 = ifelse(stat3 == "Inf",  NA,  stat3), 
         stat4 = ifelse(stat4 == "-Inf" | stat4 == "NaN",  NA,  stat4), 
         stat5 = ifelse(stat5 == "-Inf" | stat5 == "NaN",  NA,  stat5), 
         stat6 = ifelse(stat6 == "-Inf" | stat6 == "NaN",  NA,  stat6), 
         stat7 = ifelse(stat7 == "-Inf" | stat7 == "NaN",  NA,  stat7)) %>%
  select(-c(degree2))

# impute a few missing values
imp <- lm(stat3 ~ stat4 + stat5 + stat6 + stat7, data = cri2)

cri2$stat3i <- round(predict.lm(imp, newdata = cri2),0)

cri2$stat3 <- ifelse(is.na(cri2$stat3), cri2$stat3i, cri2$stat3)

cri2 <- select(cri2, -c(stat3i))




```

### Measure Difficulty and Stats-Skills

```{r measure}
m1 <- ' difficult =~  stat3
        stat_skill =~ stat4 + stat5 + stat6 + stat7
        difficult ~~ stat_skill '

cri2_nomis <- completeFun(cri2,  c("stat3", "stat4", "stat7"))

cfa <- cfa(m1,  data = cri2_nomis)

preds <- as.data.frame(lavaan::lavPredict(cfa,  newdata = cri2_nomis))

cri2_nomis <- cbind(cri2_nomis,  preds)

cri2_nomis <- select(cri2_nomis,  u_teamid,  difficult,  stat_skill)

cri2 <- left_join(cri2,  cri2_nomis,  by = "u_teamid")

# mean replacement (don't use, too risky)

# cri2 <- cri2 %>%
#  mutate(difficult = ifelse(is.na(difficult),  mean(difficult,  na.rm = T),  difficult), 
#         stat_skill = ifelse(is.na(stat_skill),  mean(stat_skill,  na.rm = T),  stat_skill))

rm(cri2_nomis,  preds,  cfa)

```


### Merge

```{r merge_two}

# teamsize unfortunately not in these data
teamsize <- read.csv(file = "data/teamsize.csv",  header = T)

cri2 <- left_join(cri2,  teamsize,  by = "u_teamid")

# select only needed vars

cri2 <- dplyr::select(cri2,  u_teamid,  u_expgroup1,  backgr_degree1, backgr_degree2, backgr_degree3,  numinteam,  software_final_models,  degree, difficult,  stat_skill)


# add instances of routine reseracher variability
routine <- read.csv(file = "data/routine_var.csv", header = F)

colnames(routine) <- c("routine","u_teamid")
routine$routine <- as.numeric("1")


cri2 <- left_join(cri2, routine, by = "u_teamid")
cri2$routine <- ifelse(is.na(cri2$routine), 0, cri2$routine)

cri <- left_join(cri,  cri2,  by = "u_teamid")

cri_cur <- left_join(cri_cur,  cri2,  by = "u_teamid")

rm(teamsize,  routine, cri2)

```

### Replication Results

It is necessary to convert them into long form for plotting and analysis. Also, not that u_teamid2 keeps the two teams that submitted separate analyses by wave as distinct teams for now (team 70 and 101)


```{r results}

columns <- c("x", "Exp1", "oa10", "s10", "dif10", "oa20", "s20", "dif20", "oa30", "s30", "dif30", "oa40", "s40", "dif40", "oa50", "s50", "dif50", "oa55", "s55", "dif55", "oa60", "s60", "dif60", "oa65", "s65", "dif65", "oa70", "s70", "dif70", "oa75", "s75", "dif75", "oa80", "s80", "dif80", "oa85", "s85", "dif85", "oa90", "s90", "dif90", "oa97", "s97", "dif97", "oa100", "s100", "dif100", "oa107", "s107", "dif107", "oa110", "s110", "dif110", "oa117", "s117", "dif117", "oa120", "s120", "dif120", "oa127", "s127", "dif127", "oa131", "s131", "dif131", "oa141", "s141", "dif141", "oa151", "s151", "dif151", "oa161", "s161", "dif161", "oa175", "s175", "dif175", "oa171", "s171", "dif171", "oa185", "s185", "dif185", "oa181", "s181", "dif181", "oa195", "s195", "dif195", "oa191", "s191", "dif191", "oa205", "s205", "dif205", "oa201", "s201", "dif201", "oa217", "s217", "dif217", "oa211", "s211", "dif211", "oa227", "s227", "dif227", "oa221", "s221", "dif221", "oa237", "s237", "dif237", "oa231", "s231", "dif231", "oa247", "s247", "dif247", "oa241", "s241", "dif241", "oa400", "s400", "dif400", "oa401", "s401", "dif401", "oa390", "s390", "dif390", "oa391", "s391", "dif391", "oa380", "s380", "dif380", "oa381", "s381", "dif381", "oa370", "s370", "dif370", "oa371", "s371", "dif371", "u_teamid", "u_teamid2", "u_expgroup1", "backgr_degree1", "backgr_degree2", "backgr_degree3", "numinteam", "software_final_models", "degree", "difficult", "stat_skill","routine")

colnames(cri) <- columns
colnames(cri_cur) <- columns

# from wide to long
cri_long <- reshape(as.data.frame(cri), varying = c("oa10", "s10", "dif10", "oa20", "s20", "dif20", "oa30", "s30",  "dif30", "oa40", "s40", "dif40", "oa50", "s50", "dif50", "oa55", "s55", "dif55", "oa60", "s60", "dif60", "oa65", "s65", "dif65", "oa70", "s70", "dif70", "oa75", "s75", "dif75", "oa80", "s80", "dif80", "oa85", "s85", "dif85", "oa90", "s90", "dif90", "oa97", "s97", "dif97", "oa100", "s100", "dif100", "oa107", "s107", "dif107", "oa110", "s110", "dif110", "oa117", "s117", "dif117", "oa120", "s120", "dif120", "oa127", "s127", "dif127", "oa131", "s131", "dif131", "oa141", "s141", "dif141", "oa151", "s151", "dif151", "oa161", "s161", "dif161", "oa175", "s175", "dif175", "oa171", "s171", "dif171", "oa185", "s185", "dif185", "oa181", "s181", "dif181", "oa195", "s195", "dif195", "oa191", "s191", "dif191", "oa205", "s205", "dif205", "oa201", "s201", "dif201", "oa217", "s217", "dif217", "oa211", "s211", "dif211", "oa227", "s227", "dif227", "oa221", "s221", "dif221", "oa237", "s237", "dif237", "oa231", "s231", "dif231", "oa247", "s247", "dif247", "oa241", "s241", "dif241", "oa400", "s400", "dif400", "oa401", "s401", "dif401", "oa390", "s390", "dif390", "oa391", "s391", "dif391", "oa380", "s380", "dif380", "oa381", "s381", "dif381", "oa370", "s370", "dif370", "oa371", "s371", "dif371"),  
                    idvar = "u_teamid2",  
                    direction = "long",  
                    v.names = c("oa","s","dif"),
                    sep = "")

cri_cur_long <- reshape(as.data.frame(cri_cur), varying = c("oa10", "s10", "dif10", "oa20", "s20", "dif20", "oa30", "s30",  "dif30", "oa40", "s40", "dif40", "oa50", "s50", "dif50", "oa55", "s55", "dif55", "oa60", "s60", "dif60", "oa65", "s65", "dif65", "oa70", "s70", "dif70", "oa75", "s75", "dif75", "oa80", "s80", "dif80", "oa85", "s85", "dif85", "oa90", "s90", "dif90", "oa97", "s97", "dif97", "oa100", "s100", "dif100", "oa107", "s107", "dif107", "oa110", "s110", "dif110", "oa117", "s117", "dif117", "oa120", "s120", "dif120", "oa127", "s127", "dif127", "oa131", "s131", "dif131", "oa141", "s141", "dif141", "oa151", "s151", "dif151", "oa161", "s161", "dif161", "oa175", "s175", "dif175", "oa171", "s171", "dif171", "oa185", "s185", "dif185", "oa181", "s181", "dif181", "oa195", "s195", "dif195", "oa191", "s191", "dif191", "oa205", "s205", "dif205", "oa201", "s201", "dif201", "oa217", "s217", "dif217", "oa211", "s211", "dif211", "oa227", "s227", "dif227", "oa221", "s221", "dif221", "oa237", "s237", "dif237", "oa231", "s231", "dif231", "oa247", "s247", "dif247", "oa241", "s241", "dif241", "oa400", "s400", "dif400", "oa401", "s401", "dif401", "oa390", "s390", "dif390", "oa391", "s391", "dif391", "oa380", "s380", "dif380", "oa381", "s381", "dif381", "oa370", "s370", "dif370", "oa371", "s371", "dif371"),  
                    idvar = "u_teamid2",  
                    direction = "long",
                    v.names = c("oa","s","dif"),
                    sep = "")


rm(columns)
```

### Long form

```{r final_clean}
# gen DVs

# update colnames

colnames(cri_long) <- c("x","Exp1","u_teamid","u_teamid2","u_expgroup1","backgr_degree1","backgr_degree2","backgr_degree3","numinteam","software", "degree", "difficult","stat_skill", "routine", "dv_tag", "deviance","or","sig")
colnames(cri_cur_long) <- c("x","Exp1","u_teamid","u_teamid2","u_expgroup1","backgr_degree1","backgr_degree2","backgr_degree3","numinteam","software","degree", "difficult","stat_skill", "routine", "dv_tag", "deviance", "or","sig")

# make original study a value in each row

cri_long_orig <- subset(cri_long, u_teamid2 == 200 | u_teamid2 == 300)


cri_long_orig <- select(cri_long_orig, Exp1, dv_tag, or, sig)


colnames(cri_long_orig) <- c("Exp1","dv_tag","orig_or","orig_sig")


cri_long <- left_join(cri_long, cri_long_orig, by = c("dv_tag","Exp1"))

cri_cur_long <- left_join(cri_cur_long, cri_long_orig, by = c("dv_tag","Exp1"))

rm(cri_long_orig)


```
## Create Verification Measures

The goal is to produce three metrics

|Metric|Definition|Measure|
|------|----------|---------|
|*Verification* (verif)| The direction of the regression coefficient is the same as the original & either within 0.05 absolute difference or the same significance at p<0.05 threshold|1=verified, 0=not|
|*Exact Verification* (exact)|The value of the replication odd-ratio is identical to the second decimal place of the original|1=exact, 0=not|
|*Replication Deviance* (deviance_abs)|The absolute deviation of the replication from the original|continuous measure starting from exact (=0) and increasing positive values|


```{r dvs, warning = F, message = F}
cri_long <- cri_long %>%
  mutate(or = round(as.numeric(or),3),
         orig_or = round(as.numeric(orig_or),3))

cri_cur_long <- cri_cur_long %>%
  mutate(or = round(as.numeric(or),3),
         orig_or = round(as.numeric(orig_or),3))

# Verification

# construct measure for positive or negative coefficient
cri_long <- cri_long %>%
  mutate(orig_direction = ifelse(is.na(orig_or), NA, ifelse(orig_or > 1, 1, ifelse(orig_or < 1, 2, 3))),
         rep_direction = ifelse(is.na(or), NA, ifelse(or > 1, 1, ifelse(or < 1, 2, 3))),
         verif = ifelse(is.na(orig_or), NA,ifelse(orig_direction == rep_direction, 1, 0)),
         exact = ifelse(is.na(orig_or), NA,ifelse(abs(deviance) < 0.01, 1, 0)),
         verif = ifelse(verif == 0 & exact == 1, 1, verif), # this corrects studies that are 1.001 and 0.999 for example which would otherwise be coded wrong in exact
         verif = ifelse(verif == 0 & sig == 0 & orig_sig == 0, 1, verif)) # this corrects for studies that are close to odd-ratio of 1 (so effect of zero), but in both original and replication are insignificant, meaning that it is a verification (roughly zero & ns in both cases)

# construct measure for positive or negative coefficient
cri_cur_long <- cri_cur_long %>%
  mutate(orig_direction = ifelse(is.na(orig_or), NA, ifelse(orig_or > 1, 1, ifelse(orig_or < 1, 2, 3))),
         rep_direction = ifelse(is.na(or), NA, ifelse(or > 1, 1, ifelse(or < 1, 2, 3))),
         verif = ifelse(is.na(orig_or), NA, ifelse(orig_direction == rep_direction, 1, 0)),
         exact = ifelse(is.na(orig_or), NA, ifelse(abs(deviance) < 0.01, 1, 0)),
         verif = ifelse(verif == 0 & exact == 1, 1, verif),
         verif = ifelse(verif == 0 & sig == 0 & orig_sig == 0, 1, verif))
```

```{r absdev}
# remove teams without results

cri_long <- completeFun(cri_long, "or")
cri_cur_long <- completeFun(cri_cur_long, "or")

#create absolute deviance

cri_long <- cri_long %>%
  mutate(deviance_abs = abs(deviance))

cri_cur_long <- cri_cur_long %>%
  mutate(deviance_abs = abs(deviance))

cri_long <- cri_long[order(cri_long$Exp1,cri_long$deviance_abs),]

cri_cur_long <- cri_cur_long[order(cri_cur_long$Exp1,cri_cur_long$deviance_abs),]

cri_long <- cri_long %>%
  group_by(Exp1) %>%
  mutate(count = row_number(),
         count = count/1000,
         max = max(count, na.rm = T),
         max1 = ifelse(Exp1 == 1, max, NA))

cri_cur_long <- cri_cur_long %>%
  group_by(Exp1) %>%
  mutate(count = row_number(),
         count = count/1000,
         max = max(count, na.rm = T),
         max1 = ifelse(Exp1 == 1, max, NA))

# make highest count value equal in both groups
cri_long <- cri_long %>%
  mutate(Exp1 = as.factor(Exp1),
         max1 = max(cri_long$max1, na.rm=T),
         max = max(cri_long$max, na.rm=T),
         count = ifelse(Exp1 == 1, round((max/max1)*count,3), count))
         
cri_cur_long <- cri_cur_long %>%
  mutate(Exp1 = as.factor(Exp1),
         max1 = max(cri_long$max1, na.rm=T),
         max = max(cri_long$max, na.rm=T),
         count = ifelse(Exp1 == 1, round((max/max1)*count,3), count))

# relevel to have transparent group first

cri_long$Exp1 <- relevel(cri_long$Exp1, "1")
cri_cur_long$Exp1 <- relevel(cri_cur_long$Exp1, "1")


# create an in sample code (without original study and with non-convergence removed)
cri_long$insamp <- ifelse(cri_long$u_teamid == 200 | cri_long$u_teamid == 300, NA, 1)
cri_long$insamp <- ifelse(cri_long$or == "speci", NA, cri_long$insamp)

cri_cur_long$insamp <- ifelse(cri_cur_long$u_teamid == 200 | cri_cur_long$u_teamid == 300, NA, 1)
cri_cur_long$insamp <- ifelse(cri_cur_long$or == "speci", NA, cri_cur_long$insamp)

# stats background

cri_long <- cri_long %>%
  mutate(backgr_degree2 = ifelse(is.na(backgr_degree2), 6, backgr_degree2),
         backgr_degree3 = ifelse(is.na(backgr_degree3), 6, backgr_degree3),
         stat_degree = ifelse(backgr_degree1 == 7, 1, ifelse(backgr_degree2 == 7, 1, ifelse(backgr_degree3 == 7, 1, 0))))
         
cri_cur_long <- cri_cur_long %>%
  mutate(backgr_degree2 = ifelse(is.na(backgr_degree2), 6, backgr_degree2),
         backgr_degree3 = ifelse(is.na(backgr_degree3), 6, backgr_degree3),
         stat_degree = ifelse(backgr_degree1 == 7, 1, ifelse(backgr_degree2 == 7, 1, ifelse(backgr_degree3 == 7, 1, 0))))         
         


# stata dummy

cri_long$stata <- ifelse(cri_long$software == "Stata", 1, 0)
cri_cur_long$stata <- ifelse(cri_cur_long$software == "Stata", 1, 0)

#remove original study from data
cri_long <- subset(cri_long, insamp == 1)
cri_cur_long <- subset(cri_cur_long, insamp == 1)

# Team 33 missing data on stat degree, code to 0
cri_cur_long$stat_degree <- ifelse(is.na(cri_cur_long$stat_degree), 0, cri_cur_long$stat_degree)

# Make soc degree variable (versus Poli Sci and Other)
cri_cur_long$degree_soc <- ifelse(is.na(cri_cur_long$degree), 3, cri_cur_long$degree)

cri_cur_long$degree_soc <- ifelse(cri_cur_long$degree_soc == 1, 1, 0)

cri_long$degree_soc <- ifelse(is.na(cri_long$degree), 3, cri_long$degree)

cri_long$degree_soc <- ifelse(cri_long$degree_soc == 1, 1, 0)


```




## Save Data

```{r save}
save.image(file = "data/data.Rdata")
```

